A Data-Driven Framework for Neural Field Modelling

### 2010-10-31 ltx/first_order_framework/LaTeX_Manuscript.tex
changes to state and parameter estimates

\parham{To further study the ability of the proposed technique we used differents sets of connectivity basis functions parameters. The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).

@@

\subsection{Implications for Experiment Design}
As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation, where the mean parameter estimates are in good agreement with the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.

>>>>

\parham{To further study the ability of the proposed technique we used different sets of connectivity basis functions parameters. The reconstructed connectivity kernels from the estimated parameters are shown in Figure~\ref{fig:Figure8}, where for each subset the mean over the 50 realisations is shown as a dotted line and the 95\% confidence interval is indicated by the grey shaded region.} \parham{this bit should change as well:} The figure verifies that the shape of the estimated connectivity kernel is in good accordance with the true kernel. The true kernel lies within the confidence interval; however, the mean estimated kernel is more negative than the actual kernel due to the small bias in the estimates of the inhibitory parameter, $\hat\theta_1$, as seen in Figure~\ref{fig:Figure7}(C).

\parham{variations in thereshold and slope}

\parham{variations in sensor width}

@@

\subsection{Implications for Experiment Design}
As seen in Figure~\ref{fig:Figure7}, the results indicate accurate estimation \parham{for the connectivity kernel parameters}, where the mean parameter estimates are in good agreement with the actual values. The estimates of the connectivity kernel parameters show relatively broad distributions, which can be expected considering the system's input is modelled as a random disturbance, and the observations are corrupted by noise. To overcome the effect of noise, the use of a controlled input stimulus should be considered when applying the estimation algorithm to electrophysiological recordings. Given knowledge of the input and the appropriate model, it is expected that the variance of the parameter estimates will decrease. Even when using an input, our results imply that we should only expect to learn distributions of parameters, rather than uncover a `true' parameter set. By designing an input signal carefully and using an evoked-potential paradigm, where stimuli are repeated many times, data could be epoched into (and averaged over) a sufficient number of trials (realisations), where each trial is a response to a stimulus, such that a distribution of the parameter estimates can be formed.
